---
title: "My first MD"
author: "Timothee Bonnet"
date: "23 August 2019"
output:
  html_document:
    highlight: kate
    theme: cerulean
    toc: yes
    toc_float: yes
---

# Introduction

Normal, *italics*, **bold**, _**both**_, _italics_

- q 
- s
- s

```{r echo=TRUE, cache=TRUE}
par(mfrow=c(1,2))
x1 <- rnorm(200)
x2 <- x1 +rnorm(200)
y <- 1 + x1 +rnorm(200)
summary(lm(y ~ x2))
plot(x2, y)
plot(x2, y)
```

the result is `r rnorm(1)` 

` 1 + pi `

`r 1 + pi `

```{r, echo=TRUE, eval=FALSE}
lm(y ~ x)
```

```{r, echo=FALSE, eval=TRUE}
#load("lm")
  for()
  {
    er 
    {
      
    }
  }
```


$a^2 + b = 1$

$$
a + d + e\\
q= \sum
$$

```{r}
data(cars)
knitr::kable(x = head(cars), caption = "A knitr kable table")
```

## Blabla

### subsubsection
#### subsubsubsection
##### subsubsubsubsection
###### subsubsubsubsubsection


## Linear regression {.tabset}
### Simple
A simple regression measures total associations
```{r}
summary(lm(y ~ x2))
```

### Multiple
A multiple regression measures direct associations, corrected for indirect
associations.
```{r}
summary(lm(y ~ x1+x2))
```

### Multiple
A multiple regression measures direct associations, corrected for indirect
associations.
```{r}
summary(lm(y ~ x1+x2))
```

eohohr


## Linear regression again